Improved Bounds for Online Balanced Repartitioning

### 2020-04-02 paper/paper.tex
On cascade

\section{Perfect Partition reachable within one swap}

@@

\section{Dynamic Graph Bisection (two clusters case)}

>>>>

\section{Maciek's sketches}

\subsection{Cascade}

For now, assume $\alpha=1$ (not to deal with inter-component communication).
Consider an algorithm DET2, a modified version of DET from \cite{repartition-disc}.
Modification is the following: when repartition is necessary, move to \emph{the closest} perfect partition of components.

\begin{theorem}
  A single repartition of DET2 migrates nodes among at most $p(k)^2+k$ clusters, where $p(k)$ is the number of integer partitions $k$.
  The corollary is, the cost of the repartition is bounded by $O(k \cdot \alpha \cdot e^{c\cdot \sqrt{k}})$ for a constant $c$.
\end{theorem}

\subsection{Perfect Partition reachable within one swap}

\maciek{Best to include it in the improved LB omega(lk) to help increase the lb by k-1}

@@
